Classless Java

### 2015-09-17 paper/sections/Overview.tex
Automatic return type refinement for with, clone methods.

\lstinputlisting[linerange=33-45]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINT

@@

\lstinputlisting[linerange=82-112]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINTIMPL

@@

\lstinputlisting[linerange=50-77]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINT_OF

>>>>

\lstinputlisting[linerange=33-42]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINT

@@

\lstinputlisting[linerange=81-111]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINTIMPL

@@

\lstinputlisting[linerange=47-76]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINT_OF
